---
title: "Fries"
author: "Brandon, Casey and Alex"
date: '2022-04-01'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
fries <- read.csv("fries.csv")
```

## Introduction

What question are we trying to answer "operationalize"

What does a French fry look like at different fast food chains We measured weight, length, and both widths of fries from multiple fast food locations.

## Methodology and Data Collection


Fries were  collected. These were the prices and weights:

- McDonald's Large Fries
  - 6.53oz
  - $3.68 (with tax)
	
- Wendy's Large Fries
  - 6.35oz
  - $3.13 (with tax)

- Burger King Large Fries
  - 6.42oz
  - $3.29 (without tax)

- Carl's Jr. Large Fries
	- 5.33oz
	- $
	
	
Weight was collected on a digital kitchen scale. Weights were collected in ounces and it was determined the scale is accurate to grams. The grams are converted in the scale to ounces.

How we collected data

The steps we will take to evaluate the data

## Data Analysis
All that fancy stats stuff

If you want to get data from just one place do something like 

`r justWendys <- subset(fries, Business== "Wendys")`



```{r, echo=FALSE}
ggplot(fries) +
  geom_density(aes(x=Length, fill=Business), alpha=0.4) +
  labs(
    title="Length of Fries",
    x="Length (mm)"
  ) +
  theme_gray()

```

```{r, echo=FALSE, warning=FALSE}

ggplot(fries) +
  geom_density(aes(x=Grams, fill=Business), alpha=0.5, adjust=1.9) +
  labs(
    title="Weight of Fries",
    x="Wight (grams)"
  ) +
  theme_gray()

#adjust 1.9 smoothes the discrete values into a normal looking graph.
```



## Conclusions
