---
title: "Fries"
author: "Brandon, Casey and Alex"
date: '2022-04-01'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
fries <- read.csv("fries.csv")
```

## Introduction

What question are we trying to answer "operationalize"

What does a French fry look like at different fast food chains We measured weight, length, and both widths of fries from multiple fast food locations.

## Methodology and Data Collection

Weight was collected on a digital kitchen scale. Weights were collected in ounces and it was determined the scale is accurrate to grams. The grams are converted in the scale to ounces.

How we collected data

The steps we will take to evaluate the data

## Data Analysis
All that fancy stats stuff

```{r, echo=FALSE}
ggplot(fries) +
  geom_density(aes(x=Length, fill=Business), alpha=0.4) +
  labs(
    title="Length of Fries",
    x="Length (mm)"
  ) +
  theme_gray()

```

```{r, echo=FALSE, warning=FALSE}

ggplot(fries) +
  geom_density(aes(x=Grams, fill=Business), alpha=0.5, adjust=1.5) +
  labs(
    title="Weight of Fries",
    x="Wight (grams)"
  ) +
  theme_gray()
```



## Conclusions
